Deterministic contention management for low latency Cloud RAN over an optical ring

### 2019-01-18 v3/articleV3.tex
début derniere section

\subsection{Valid assignment with small C-RAN latency}
\label{sec:maxant}

The previous approach limits the number of antennas supported by the ring when $P-RS \mod ET \neq 0$, which is the case with N-GREEN parameters. In order to maximize the number of supported antennas (and to minimize the reserved containers), we now \emph{allow the data from an RRH to use different positions}.

\todo{dire le tradoff -> en échange de plus d'antennes et d'une meilleure latence BE on a une 
petite perte sur les C-Rans et une augmentation raisonnable de complexité (buffering pour les CRAN).}

>>>>

\subsection{Valid assignment with additional C-RAN latency}
\label{sec:maxant}

The previous approach limits the number of antennas supported by the ring when $P-RS \mod ET \neq 0$, which is the case with N-GREEN parameters. In order to maximize the number of supported antennas, we now \emph{allow the data from an RRH to use different positions}. The method we present in this section enables us to support more antennas and improves the latency of BE traffic (it reserves less free containers)
by \emph{allowing the data from an RRH to use different positions}.
It is a the cost of a slightly worse latency for C-RAN traffic and it requires to implement some buffering for the C-RAN containers.
